Lightweight Real-Time Feature Monitoring

### 2020-07-15 chapters/conclusions.tex
Added Sliding Bloom and Sliding CMS to references, mention only

>>>>

Besides testing new methods for distribution divergence measurement or multiple test correction methods, we have a set of parameters to work with. Experiments where only one of the parameters is changed should be carried out. Our method has lots of parameters to fine tune and experiment with, as defined in Section \ref{sec:batch-phase}, such as the tuple-based half-life, the size of the samples we make, the $\gamma$ probability (which defines the probability of not having at least one sample divergence measure in the upper tail of the distribution) and the Family-Wise Error Rate.

### 2020-07-15 chapters/sota.tex
EMA hist pseudocode and Final remarks analysis
Added Sliding Bloom and Sliding CMS to references, mention only

\subsubsection{SAMM: Automatic Model Monitoring for Data Streams}

@@

%\subsection{Sliding Bloom Filter}
%\subsection*{Data Structure}
%\subsection*{Element Insertion}
%\subsection*{Element Eviction}
%\subsection*{Time complexity analysis}
%\subsection*{Space complexity analysis}
%\subsection*{Applicability to our Hypothesis}

%\subsection{Sliding Count-Min Sketch}
%\subsection*{Data Structure}
%\subsection*{Element Insertion}
%\subsection*{Element Eviction}
%\subsection*{Time complexity analysis}
%\subsection*{Space complexity analysis}
%\subsection*{Applicability to our Hypothesis}

@@

We then discussed probabilistic data structures (Section \ref{sec:pds}) and their sliding window implementations (Section \ref{sec:sliding-pds}). Despite being efficient, both time and memory-wise, each probabilistic data structure allows for one type of aggregation, and none of them happened to be of particular use to us.

>>>>

\subsubsection{SAMM: Automatic Model Monitoring for Data Streams} \label{sec:SAMM}

@@

@@

In Section \ref{sec:pds}, we discussed probabilistic data structures. Then, in Section \ref{sec:sliding-pds}, we explored some probabilistic data structure sliding window implementations. We explored only sliding window versions of the HyperLogLog, but sliding versions of other probabilistic data structures exist, such as the Sliding Bloom Filter \cite{SlidingBloom} and the Sliding Count-Min Sketch \cite{SlidingCMS}. Despite being efficient, both time and memory-wise, each probabilistic data structure allows for one type of aggregation, and none of them happened to be of particular use to us.
